MSF_Groupwork-NBA_shotlog

### 2016-10-11 MSFGroupwork-NBAHotHand.Rmd
add notes

---
title: "MSF_Groupwork-NBA_shotlog" 
author: "Team_9"
output: html_document  ---
  title: "MSF_Groupwork-NBA_shotlog"
author: "Team_9"
output: html_document 
---

@@

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory (Artemis)
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate 
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i.

@@

## Installing libraries

```{r}
install.packages('reshape')

@@

## Calling libraries
```{r}
library(reshape)
library(ggplot2)

@@

# accuracy for Top 10 scoring players

@@

df[, "ACC_P_SEC"] <- as.numeric()

#Assign accuracy per second to main dataframe
for (i in 1:nrow(df)){
  for (j in 1:23){
    if (df$SHOT_CLOCK[i] >j & df$SHOT_CLOCK[i] <= j+1 & df$SHOT_CLOCK[i] != 99) df[i, "ACC_P_SEC"] <- acc[j, "Accuracy"]
  }
}

cov(df$ACC_P_SEC, df$SHOT_CLOCK)
cor.test(df$ACC_P_SEC, df$SHOT_CLOCK)

@@

#

```{r}
# Find shooting percentage of each match

# Trying to reshape...

library(reshape)
game <- cast(data = df, GAME_ID1 ~ SHOT_RESULT)
View(game)

#

Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
for(i in 21400001:21400908){
  j = i - 21400001 +1 # 
  game <- df[, df[, "GAME_ID1"] == i]
  home <- game[, game["LOCATION"] == "H"]
  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
  away <- game[, game["LOCATION"] == "A"]
  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
  FG_Percentage[j] <- home.p
  FG_Percentage[j + 1] = away.p
  Team[j] = "H"
  Team[j + 1] = "A"
}

@@

I   What would be the next steps?
---

>>>>

---
title: "MSF_Groupwork-NBA_shotlog" 
author: "Team_9"
output:
  pdf_document: default
  html_document: default
---

@@

##Introduction
I   What is your theme or research question?
a. Hot Hand Theory (Artemis)
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate 
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i.

##Theory
I   What do you expect to find?
a.

##Methods
I   Describe the dataset:

    Data on shots taken during the 2014-2015 season, who took the shot, where on the floor was the shot taken from, who was the nearest defender, how far away was the nearest defender, time on the shot clock, and much more. The column titles are generally self-explanatory.
Useful for evaluating who the best shooter is, who the best defender is, the hot-hand hypothesis, etc.
Scraped from NBA's REST API.  It has 128,609 rows and 22 columns with 16 MB data size. ##TO BE UPDATED FURTHER

@@

    The dataset comprise of comprehensive observational data to start to work with.

I   Limitations
    The dataset consists only for 1 year NBA season with regular match (82 matches per team for both home and away matches). The playoff and other matches during the year is not included.

##Analysis

### Installing libraries

```{r}
#install.packages('reshape')

@@

### Calling libraries
```{r}
library(reshape)
library(ggplot2)

@@

@@

@@

# Find shooting percentage of each match

```{r}
# Reshape the dataframe

game <- cast(data = df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + LOCATION + player_name + W ~ FGM)

# Field Goal Attempts

game[, "FGA"] <- NA
for(i in 1:nrow(game)){
  game[i, "FGA"] <- game[i, "1"] + game[i, "0"]
}

# Find Feild Goal Percentage of each indivudual player in that match

game[, "FG.percentage"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG.percentage"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}
```

# Impact of Super Star Players

```{r}

# Pick out 8 of the best players in that regular season and create a new subset. Analyse how shooting percentage of these players can influence the result of a match.

super.star.list <- c("lebron james", "james harden", "russell westbrook", "stephen curry", "anthony davis", "blake griffin", "klay thompson", "lamarcus aldridge") # players picked out
super.star <- game[game$player_name %in% super.star.list, c("player_name", "W", "FGA", "FG.percentage")] # create a subset for these players

ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))
ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W))

# Replace "W" and "L" with 1 and 0 respectively, 
super.star[, "W"] <- as.character(super.star[, "W"])
for (i in 1:nrow(super.star)) {
  if (super.star[i, "W"] == "W") super.star[i, "W"] <- 1
  if (super.star[i, "W"] == "L") super.star[i, "W"] <- 0
}
super.star[, "W"] <- as.numeric(super.star[, "W"])

# Correlation test
t.test(super.star[, "W"], super.star[, "FGA"]) # this makes no sense...

# Linear regression
summary(lm(W ~ player_name + FGA, data = super.star))
summary(lm(W ~ player_name + FG.percentage, data = super.star))

@@

knitr::opts_chunk$set(echo = TRUE)
```
Justin Leiendecker, Alexander Romanenko, Artmeis Tomadaki-Balomenou, Zijun Wei, Reza Widodo
